### 2017-12-08 submission/manuscript.Rmd
add results template write up

***Per Base Error Rate is Dependent on both Taq and Cycle Number Used:***

***Chimeric Sequences are HiFi Taq Dependent:***

>>>>

***Per Base Error Rate is Dependent on both Taq and Cycle Number Used:***
The median average per base error was highest for the Kappa HiFI Taq [FIgure 3A]. Sub-sampling depth seems to have little effect on this rate with both 5000 and 10000 sub-sampled sequences showing similar results [Figure 3B & C]. Generally, there were small differences between the various HiFi Taq at lower cycle number but larger differences at higher cycle number [Figure 3B & C]. Platinum HiFi Taq consistently had the highes median average per base error rate while Phusion and Accuprime had the lowest [Figure 3B & C]. These differences though were realtively small between the different HiFi Taq [Figure 3]. The total seqeunces with at least one error matched the median average per base error except for the Accuprime HiFi Taq [Figure S1]. Although it had the lowest per base error rate it had either the largest or second largest number of sequences with at least one error regardless of cycle number of sub-sampling depth [Figure S1]. Investigation of whether there were Taq dependent effects on base subsitution found that there was no clear bias and this was indpendent of sub sampling depth [Figure S2-S4]. Further, the variation in subsitution error seems to reduce as the sequencing depth increases [Figure S2-S4].

***Chimeric Sequences are HiFi Taq Dependent:***
After chimera removal using VSEARCH and removal of sequences that did not classify as bacteria we assessed the percentage of sequences that were still chimeric within our mock community. From this we observed that Platinum HiFi conssitently had the highest percentage of chimeric reads regardless of amplification cycle number and sub-sampling depth [Figure 4]. These results mirror the observations of increased number of OTUs and the increased median average per base error [Figure 2-4].
